On the discovery and origin of $r$-process stars in the Milky Way

### 2018-03-01 article/ms.tex
arrange other co-auths alphabetically and add JBH

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[Matthew T. Miles et al.]{Matthew T. Miles,$^{1}$\thanks{E-mail: mtmil3@student.monash.edu}
	Andrew R. Casey,$^{1,2}$
	Brodie J. Norfolk,$^{1}$
	Alex J. Kemp,$^{1}$\newauthor
	John C. Lattanzio,$^{1}$
	Kevin C. Schlaufman,$^{3}$
	Alexander P. Ji,$^{4}$
	Anna Y. Q. Ho$^{5}$
	\\
	% List of institutions
	$^{1}$School of Physics and Astronomy, Monash University, Clayton Campus, Victoria 3800, Australia\\
	$^{2}$Faculty of Information Technology, Monash University, Clayton Campus, Victoria 3800, Australia\\
	$^{3}$Department of Physics and Astronomy, Johns Hopkins University, 3400 N Charles St., Baltimore, MD 21218, USA\\
	$^{4}$Department of Physics and Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, Cambridge, MA 02139, USA\\
	$^{5}$Cahill Center for Astrophysics, California Institute of Technology, MC 249-17, 1200 E California Blvd, Pasadena, CA, 91125, USA
}

>>>>

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[Matthew T. Miles et al.]{Matthew T. Miles,$^{1}$\thanks{E-mail: mtmil3@student.monash.edu}
	Andrew R. Casey,$^{1,2}$
	Brodie J. Norfolk,$^{1}$
	Alex J. Kemp,$^{1}$\newauthor
    Joss Bland-Hawthorn?,$^3$
    Anna Y. Q. Ho?,$^4$
    Alexander P. Ji?,$^5$
	John C. Lattanzio?,$^{1}$
	Kevin C. Schlaufman?,$^{6}$
	\\
	% List of institutions
	$^{1}$School of Physics and Astronomy, Monash University, Clayton Campus, Victoria 3800, Australia\\
	$^{2}$Faculty of Information Technology, Monash University, Clayton Campus, Victoria 3800, Australia\\
    $^{3}$Sifa, University of Sydney\\
	$^{4}$Cahill Center for Astrophysics, California Institute of Technology, MC 249-17, 1200 E California Blvd, Pasadena, CA, 91125, USA\\
    $^{5}$Carnegie Observatories\\
    $^{6}$Department of Physics and Astronomy, Johns Hopkins University, 3400 N Charles St., Baltimore, MD 21218, USA
}
